### 2023-04-13 latex/CommStyle.tex
included testimonia

\linespread{1}
\setlength{\parskip}{0.3em}
\setlength\parindent{0pt}
\setlength{\vindent}{0pt}
\def\startverse{\begin{ekdverse}\begin{itshape}}
\def\endverse{\normalsize\end{itshape}\end{ekdverse}} % \textup
\setvnum{}

>>>>

\linespread{1}
\setlength{\parskip}{0.3em}
\setlength\parindent{0pt}
\setlength{\vindent}{0pt}
\def\startverse{\begin{ekdverse}\begin{itshape}} %%% marked for change 2023-04-13 mm
\def\endverse{\normalsize\end{itshape}\end{ekdverse}} % \textup %%% marked for change 2023-04-13 mm
\NewDocumentEnvironment{versinnote}{O{}}{\begin{ekdverse}\begin{itshape}}{\end{itshape}\end{ekdverse}} %%% change 2023-04-13 mm
\setvnum{}
